Stepwise Multiple Regressions

### 2021-02-04 Stepwise Multiple Regressions.Rmd
a typo
simple change

#Fit the full model
Full_Model <- lm(effect ~., data = y)

#Stepwise model
step.model <- stepAIC(Full_Model, direction = "both", 
                      trace = FALSE)

>>>>

#Fit the full model
Full_Model <- lm(effect ~., data = y,
                 na.action = na.omit)
summary(Full_Model)
```

```{r}
#Stepwise model
step.model <- stepAIC(Full_Model, direction = "both", 
                      trace = FALSE)
